Columnar VCF for Biobank scale datasets using Zarr

### 2024-04-26 paper.tex

%%% Use the \authfn to add symbols for additional footnotes, if any. 1 is reserved for correspondence emails; then continuing with 2 etc for contributions.
\author[1,\authfn{1},\authfn{2}]{First Author}
\author[2,\authfn{1},\authfn{2}]{Second Author}
\author[2]{Third Author}
\author[2,\authfn{1}]{Fourth Author}

\affil[1]{First Institution}
\affil[2]{Second Institution}

%%% Author Notes
\authnote{\authfn{1}abc@uni.edu; alphbeta@lab.edu}
\authnote{\authfn{2}Contributed equally.}

@@

%%% "Short" author for running page header
\runningauthor{First et al.}

@@

\begin{keywords}
Keyword1; keyword 2; keyword 3 (Three to ten keywords representing the main content of the article)
\end{keywords}
\end{frontmatter}

%%% Key points will be printed at top of second page
\begin{keypoints*}
\begin{itemize}
\item This is the first point
\item This is the second point
\item One last point.
\end{itemize}
\end{keypoints*}

>>>>

%%% Use the \authfn to add symbols for additional footnotes, if any. 
% 1 is reserved for correspondence emails; then continuing with 2 etc for contributions.
% First author
\author[1,\authfn{1}]{Eric Czech}
\author[2,\authfn{1}]{Tim Millar}
\author[3,\authfn{1}]{Tom White}

% Middle
\author[4]{Ben Jeffery}
\author[5]{Alistair Miles}
\author[6]{Sam Tallman}
\author[1]{Rafal Wojdyla}
\author[7]{Shadi Zabad}

% Senior 
\author[8,\authfn{2}]{Jeff Hammerbacher}
\author[4,\authfn{2},\authfn{3}]{Jerome Kelleher}

\affil[1]{Related Sciences}
\affil[2]{Tim's Institute}
\affil[3]{Tom's Institute}
\affil[4]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, 
University of Oxford, UK}
\affil[5]{Wellcome Sanger Institute}
\affil[6]{Genomics England}
\affil[7]{School of Computer Science, McGill University, Montreal, QC, Canada}
\affil[8]{Jeff's Institute}

%%% Author Notes
\authnote{\authfn{1}Joint first author.}
\authnote{\authfn{2}Joint senior author.}
\authnote{\authfn{3}jerome.kelleher@bdi.ox.ac.uk}

@@

%%% "Short" author for running page header
\runningauthor{Czech et al.}

@@

\begin{keywords}
Variant Call Format; Zarr; Analysis ready data.
\end{keywords}
\end{frontmatter}

%%% Key points will be printed at top of second page
\begin{keypoints*}
\begin{itemize}
\item VCF is widely supported, and the underlying data model entrenched 
in Bioinformatics pipelines.
\item The standard row-wise encoding as text (or binary) is inherently
inefficient for large-scale data processing.
\item The Zarr format provides an efficient solution, by encoding fields
in the VCF separately in chunk-compressed binary format.
\end{itemize}
\end{keypoints*}
